Hybrid platforms and bargaining

### 2023-06-15 src/presentation/io_day.qmd
Even more last-minute improvements

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by seperate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: "best case scenario"
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 p^*_{Ti} &= c_T + \mu
 $$
:::

@@

::: {.incremental}
 - **Bargaining**<br>total profits are shared according to the Shapley-value-based rule
 - **Benchmark**<br>platform can commit to any lump-sum entry fee $F_F$
:::

@@

::: {.incremental}
 - Total profits as a function of number of entrants have a simple form:
 $$
 f(N_P, N_F) = \mu \frac{N_F V_F + N_P V_P}{N_F V_F + N_P V_P + 1}
 $$
   - Satisfies the assumption for a unique equilibrium
   - Has the form $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$
   - $g$ is concave
 - Therefore,
 $$
 \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
 $$
:::

@@

::: {.fragment}
 - **Tractable model** of hybrid platforms in which **bargaining** plays a key role
   - Applicable to other settings, too (e.g. vertical markets, franchises)
:::
::: {.fragment}
 - Highlight an important aspect if hybrid platforms
   - **Hybridness increases bargaining power** against entrants
   - This can have **negative welfare consequences**
:::
::: {.fragment}
 - Policy implications for such markets
   - Amazon operating in hybrid mode
   - Microsoft acquiring Activision/Blizzard for $68bn
:::

@@

::: {.fragment}
 - In this paper
   - Endogenenize "hybridness" ($N_P$)
   - Relax separate product pricing assumption
   - Alternative benchmarks (e.g. exogeneous split)
:::
::: {.fragment}
 - Longer term
   - Endogeneize consumer entry
   - Three-sided negotiation (platform, firms, consumers)
   - Test bargaining through lab experiment
:::

>>>>

## Production
::: {.fragment}
 - Assume that the platform prices its products as if they were made by seperate, competitive sellers
   - Possible interpretation: profit-maximizing subsidiaries
   - More importantly: "best case scenario"
:::
::: {.fragment}
 - The optimal price is an additive markup rule:
 $$
 p^*_{Ti} = c_T + \mu
 $$
:::

@@

::: {.incremental}
 - **Bargaining**<br>Total profits are shared according to the Shapley-value-based rule
 - **Benchmark**<br>The platform can commit to any lump-sum entry fee $F_F$
:::

@@

::: {.incremental}
 - Total profits as a function of number of entrants have a simple form:
 $$
 f(N_P, N_F) = \mu \frac{N_F V_F + N_P V_P}{N_F V_F + N_P V_P + 1}
 $$
   - Satisfies the assumption for a unique equilibrium
   - Has the form $f(N_P, N_F) = g(\alpha N_P + \beta N_F)$
   - $g$ is concave
:::
::: {.fragment}
$$
\implies \quad \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F}
$$
:::

@@

::: {.fragment}
 - **Tractable model** of hybrid platforms in which **bargaining** plays a key role
   - Applicable to other settings, too (e.g. vertical markets, franchises)
:::
::: {.fragment}
 - Highlight an important aspect if hybrid platforms
   - **Hybrid mode increases bargaining power** against entrants
   - This can have **negative welfare consequences**
:::
::: {.fragment}
 - Policy implications for such markets
   - Amazon operating in hybrid mode
   - Microsoft acquiring Activision/Blizzard for $68bn
:::

@@

::: {.fragment}
 - Low-hanging fruit
   - Endogenenize hybrid mode ($N_P$)
   - Relax separate product pricing assumption
   - Alternative benchmarks (e.g. exogeneous split)
:::
::: {.fragment}
 - Longer term
   - Endogeneize consumer entry
   - Three-sided negotiation (platform, firms, consumers)
   - Test bargaining through lab experiment
:::
